3D Regression Heat Map Analysis of Population Study Data

### 2015-06-27 draft.tex
consistent naming of Three.js

 The front-end (left) is realized with \texttt{HTML5}/\texttt{CSS3}/\texttt{Javascript} and different Javascript libraries, such as \href{https://www.angularjs.org/}{\texttt{Angular.js}}, \href{http://threejs.org}{\texttt{Threejs}} and \href{http://d3js.org/}{\texttt{D3.js}}.

@@

The 3D plot is created using the WebGL-based \href{http://threejs.org}{\texttt{Threejs}} library.

>>>>

 The front-end (left) is realized with \texttt{HTML5}/\texttt{CSS3}/\texttt{Javascript} and different Javascript libraries, such as \href{https://www.angularjs.org/}{\texttt{Angular.js}}, \href{http://threejs.org}{\texttt{Three.js}} and \href{http://d3js.org/}{\texttt{D3.js}}.

@@

The 3D plot is created using the WebGL-based \href{http://threejs.org}{\texttt{Three.js}} library.
